quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-10 paper-quollr.Rmd
Added detourr to acknowledgment

The source code for reproducing this paper can be found at: [https://github.com/JayaniLakshika/paper-quollr](https://github.com/JayaniLakshika/paper-quollr). This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template. These `R` packages were used for this work: `cli` [@gabor2025], `dplyr` [@hadley2023], `ggplot2` [@hadley2016], `interp` (>= 1.1-6) [@albrecht2024], `langevitour` [@paul2023], `proxy`[@david2022], `stats` [@core2025], `tibble` [@kirill2023], `tidyselect` [@lionel2024], `crosstalk` [@joe2023], `plotly` [@chapman2020], `htmltools` [@joe2024], `kableExtra` [@hao2024], `patchwork` [@thomas2024], and `readr` [@hadley2024].

>>>>

The source code for reproducing this paper can be found at: [github.com/JayaniLakshika/paper-quollr](https://github.com/JayaniLakshika/paper-quollr). This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template. These `R` packages were used for this work: `cli` [@gabor2025], `dplyr` [@hadley2023], `ggplot2` [@hadley2016], `interp` (>= 1.1-6) [@albrecht2024], `langevitour` [@paul2023], `detourr` [@casper2025], `proxy`[@david2022], `stats` [@core2025], `tibble` [@kirill2023], `tidyselect` [@lionel2024], `crosstalk` [@joe2023], `plotly` [@chapman2020], `htmltools` [@joe2024], `kableExtra` [@hao2024], `patchwork` [@thomas2024], and `readr` [@hadley2024].

### 2025-12-10 paper-quollr.tex
Added detourr to acknowledgment

The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}. This article is created using \CRANpkg{knitr} \citep{yihui2015} and \CRANpkg{rmarkdown} \citep{yihui2018} in R with the \texttt{rjtools::rjournal\_article} template. These \texttt{R} packages were used for this work: \texttt{cli} \citep{gabor2025}, \texttt{dplyr} \citep{hadley2023}, \texttt{ggplot2} \citep{hadley2016}, \texttt{interp} (\textgreater= 1.1-6) \citep{albrecht2024}, \texttt{langevitour} \citep{paul2023}, \texttt{proxy}\citep{david2022}, \texttt{stats} \citep{core2025}, \texttt{tibble} \citep{kirill2023}, \texttt{tidyselect} \citep{lionel2024}, \texttt{crosstalk} \citep{joe2023}, \texttt{plotly} \citep{chapman2020}, \texttt{htmltools} \citep{joe2024}, \texttt{kableExtra} \citep{hao2024}, \texttt{patchwork} \citep{thomas2024}, and \texttt{readr} \citep{hadley2024}.

>>>>

The source code for reproducing this paper can be found at: \href{https://github.com/JayaniLakshika/paper-quollr}{github.com/JayaniLakshika/paper-quollr}. This article is created using \CRANpkg{knitr} \citep{yihui2015} and \CRANpkg{rmarkdown} \citep{yihui2018} in R with the \texttt{rjtools::rjournal\_article} template. These \texttt{R} packages were used for this work: \texttt{cli} \citep{gabor2025}, \texttt{dplyr} \citep{hadley2023}, \texttt{ggplot2} \citep{hadley2016}, \texttt{interp} (\textgreater= 1.1-6) \citep{albrecht2024}, \texttt{langevitour} \citep{paul2023}, \texttt{detourr} \citep{casper2025}, \texttt{proxy}\citep{david2022}, \texttt{stats} \citep{core2025}, \texttt{tibble} \citep{kirill2023}, \texttt{tidyselect} \citep{lionel2024}, \texttt{crosstalk} \citep{joe2023}, \texttt{plotly} \citep{chapman2020}, \texttt{htmltools} \citep{joe2024}, \texttt{kableExtra} \citep{hao2024}, \texttt{patchwork} \citep{thomas2024}, and \texttt{readr} \citep{hadley2024}.
